Sequence classifications to facilitate designing an effective intervention of motivational interview

### 2017-03-03 paper/AMIA/main.tex
added new figure for figure 1

if $p(S\rightarrow CT) > \delta $, where $\delta$ is experimentally defined threshold, the interview transcript (or a portion of it) is predicted to result in CT. To fit the model, we experimentally determined the value of $\delta$ where model provides highest F-measure with lower bias. Figure\ref{fig:delta} [this is a temporary figure, I will change it later] illustrates an example of the characteristics of Markov model by varying the value of $\delta$.

\begin{figure}[htb!]
    \centering
    \includegraphics[width=0.70\textwidth]{figures/deltadata.png}
    \caption{\textbf{Characteristics of proposed Markov model by varying the value of $\delta$}}
    \label{fig:delta}
\end{figure}

>>>>

if $p(S\rightarrow CT) > \delta $, where $\delta$ is experimentally defined threshold, the interview transcript (or a portion of it) is predicted to result in CT. To fit the model, we experimentally determined the value of $\delta$ where model provides highest F-measure with lower bias. Figure~\ref{fig:delta} illustrates an example of the characteristics of Markov model by varying the value of $\delta$. From the figure, it was observed that F-score value is not changing significantly with respect to $\delta $ from -5 to -1. This is because a bias is involved. However, F-score sharply decreased after $\delta = -0.9$. Thus, -0.9 will the optimal value of $\delta $, where F-measure is highest with lower bias.

\begin{figure}[htb!]
    \centering
    \includegraphics[width=0.70\textwidth]{figures/delta.png}
    \caption{\textbf{Characteristics of proposed Markov model by varying the value of $\delta$}}
    \label{fig:delta}
\end{figure}
